### 2016-11-21 Paper_v1.tex
some changes on materials and methods

The transcription rate ($w_{TX}$) was fixed in the ssFBA calculation as:
\begin{equation}
	w_{TX} = \left[R_{1}\left(\frac{K_{T7}}{1 + K_{T7}}\right)\left(\frac{v_{RNAP}}{l_{mRNA}}\right)\right]\left(\frac{G}{K_{TX}+G}\right)
\end{equation}
where $R_{1}$ denotes the concentration of RNA polymerase, $v_{TX}$ denotes RNA polymerase elongation rate (nt/hr),
$l_{G}$ denotes the gene length in nucleotides, $G$ denotes the gene concentration and $K_{TX}$ denotes the plasmid saturation coefficient.
The gene and protein sequence for CAT was determined from literature.
The last term in the $w_{TX}$ expression describes T7 promoter activity, where $K_{T7}$ quantifies T7 RNA polymerase binding [REFHERE].
The translation rate was formulated as:
 \begin{equation}
	w_{TL} = K_{P}\ Ribo\left(\frac{v_{Ribo}}{l_{Protein}}\right)mRNA_{SS}
\end{equation}
where $K_{P}$ denotes the polysome amplification constant, $Ribo$ denotes the ribosome concentration, $v_{Ribo}$ denotes the elongation rate of the ribosome in amino acids per hour, $l_{Protein}$ denotes the number of amino acids in the protein of interest, and $mRNA_{SS}$ denotes the mRNA concentration at steady state, equal to the transcription rate divided by the degradation rate of mRNA.

>>>>

The transcription rate ($w_{TX}$) was fixed in the ssFBA calculation as:
\begin{equation}
	w_{TX} = \left[R_{1}\left(\frac{K_{T7}}{1 + K_{T7}}\right)\left(\frac{v_{TX}}{l_{G}}\right)\right]\left(\frac{G}{K_{TX}+G}\right)
\end{equation}
where $R_{1}$ denotes the concentration of RNA polymerase, $v_{TX}$ denotes RNA polymerase elongation rate (nt/hr),
$l_{G}$ denotes the gene length in nucleotides, $G$ denotes the gene concentration and $K_{TX}$ denotes the plasmid saturation coefficient.
The gene and protein sequence for CAT was determined from literature.
The last term in the $w_{TX}$ expression describes T7 promoter activity, where $K_{T7}$ quantifies T7 RNA polymerase binding [REFHERE].
The translation rate ($w_{TL}$) was bounded by:
 \begin{equation}
	0\leq w_{TL} \leq \left[K_{P} R_{2}\left(\frac{v_{TL}}{l_{P}}\right)\right]\left(\frac{mRNA_{SS}}{K_{TL}+mRNA_{SS}}\right)
\end{equation}
where $K_{P}$ denotes the polysome amplification constant, $R_{2}$ denotes the ribosome concentration, $v_{TL}$ denotes the ribosome elongation rate (amino acids per hour),
$l_{P}$ denotes the number of amino acids in the protein of interest, and $mRNA_{SS}$ denotes the steady-state mRNA concentration:
\begin{equation}
	mRNA_{SS}\simeq\frac{w_{TX}}{\lambda}
\end{equation}where $\lambda$ denotes the mRNA degradation rate.
